A sheaf--function dictionary for algebraic tori over local fields

### 2013-08-19 shanghai.tex
Changes to the introduction and Part 2.

We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
Analogous sheaves on connected, commutative algebraic groups were first studied
by Deligne \cite{deligne:SGA4.5}, \David{more specific citation} and more recently Drinfeld has referred to such objects
as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
is a direct generalization of the sheaf--function dictionary to the case of commutative
group schemes which are not necessarily connected or finite type.  The other main use
of the term ``character sheaf'' traces back to Lusztig \cite{lusztig:85a}*{Def.~2.10}.  Most of his energy is devoted to
handling non-commutative groups; though he does define character sheaves for some
non-connected groups he restricts his attention to reductive groups with cyclic component group.
For extensions of $\ZZ/n\ZZ$ by a torus, it is not difficult to relate his Frobenius-stable character
sheaves to our quasicharacter sheaves.

We close the introduction with a more detailed description of the structure of this paper.
In Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
them as Weil sheaves with a Galois action.
Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism,
one direction of the sheaf--function dictionary.
We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
them to prove a functoriality result on the trace of Frobenius.
In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
and Weil restriction.
Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded and finite quasicharacter sheaves,
two subcategories of $\QC(G)$.  These alternate descriptions of quasicharacter sheaves play a key
role in the proof of Proposition~\ref{prop:restriction}.
In section \ref{sec:connected} we show that bounded and finite quasicharacter sheaves are the same
as standard quasicharacter sheaves when $G$ is connected, and that trace of Frobenius is an isomorphism.
We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and give a more concrete interpretation
of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
we give an isomorphism between $\QCiso{G}$ and $\Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))$.
Section~\ref{sec:etalecohom} proves a result in Galois cohomology that shows that trace of Frobenius is
an isomorphism for \'etale group schemes.
In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
induces an essentially surjective functor of quasicharacter sheaves.
Section~\ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem, that trace of Frobenius
is an isomorphism for $G$ as long as the geometric component group is finitely generated.

In Section~\ref{sec:GN} we introduce N\'eron models of tori and the Greenberg transform, which produce
group schemes over $\Fq$ from algebraic tori $T$ over $K$.
Section~\ref{sec:bdchar} then uses Theorem~\ref{thm:snake} to give a geometrization of characters of $T$
of bounded depth.
We give a reinterpretation of this result in Section~\ref{sec:quasichar}, using a limit process to simultaneously
geometrize all quasicharacters of $T$.  Sections~\ref{sec:bdchar} and \ref{sec:quasichar} also include
functoriality results that we hope to use in a future discussion of class field theory.
\Clifton{There is another section at the end of the paper, now.}
Finally, we close the paper in Section~\ref{sec:transfer} by discussing a transfer principle, which allows
a geometric transfer of characters between characteristic $p$ tori to characteristic $0$ tori.

@@

  We now show that $[\tau_\qcs{L}]$ depends only on the isomorphism class of $\qcs{L}$.
  Let $\alpha : \qcs{L} \to \qcs{L'}$ be an isomorphism and
  let $\tau$ and $\tau'$ be any cocycles representing the classes in the
  image of $\qcs{L}$ and $\qcs{L'}$ under \eqref{cohomologous}; by construction,
  $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$ 
  according to Lemma~\ref{lemma:section}.
    Now, $\varphi_x(s(x))$ is a
  non-zero scalar multiple of $s'(x)$; define $a: G(\bFq) \to \EEx$
  by $\alpha_x(s(x)) = a(x) s'(x)$.
  By the second part of condition~\ref{cs.3},
  $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$,
  \Clifton{Fix this.}
  so $\tau$ and $\tau'$ are cohomologous. This shows that
  \begin{equation}\label{pich1}
    \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*), \qquad \qcs{L}_{/\text{iso}} \mapsto [\tau_\qcs{L}]
  \end{equation}
  is well-defined.

@@

Recall that $\Fq$ is a finite field.
Let $K$ be a non-archimedean local field with residue field $\Fq$.
We place no restriction on the characteristic of $K$. 
We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
\Clifton{I think we should seriously consider replacing $d$ with $n$ in Part~2. Actually, I've just done that.}
%For any positive integer $d$, set $A_d\ceq \OK/\pK^d$.
Let $T$ be an algebraic torus over $K$.
We write $\Hom_{< n}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $n$ 
and $\Hom_{\text{qc}}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth;
we call these quasicharacters of $T(K)$, following \cite{tate:67a}*{2.3}.

@@

For any positive integer $n$, let
\[
%\begin{tikzcd}
\Gr_n : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\Fq$}\right)
%\end{tikzcd}
\]
be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^n$ with the Greenberg functor.
The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{d+1} \to \Gr_d$ 
\Clifton{Do you think I should say more about $P_{n}$?}
\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
For a given Néron model $\TT$ of $T$, set
\[
\GN{T}_n \ceq \Gr_n(\TT)
\qquad \text{and}\qquad
f_n \ceq P_n(\TT).
\]
%
Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
 \begin{enumerate}
   \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
  \labitem{(GN.1)}{smooth} $\GN{T}_n$ is a smooth commutative group scheme
  locally of finite type over $\Fq$ and the component group of $\GN{T}_n$ is
  geometrically finitely generated. 
  (In fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$,
  and the latter is finitely generated by \cite{xarles:93a}*{2.18}.)
  \labitem{(GN.2)}{truncation}
  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes.
  \end{enumerate}
%
We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.

@@

For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor promised by Proposition~\ref{prop:pullback}.
%
%\begin{proposition}\label{prop:nm}
The functor $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ is full and faithful.
%\end{proposition}
%
%\begin{proof}
%It suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$. Base change along $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a closed immersion of schemes $\TT_{n+1} \hookrightarrow \TT_n$ (not a morphism of group schemes). Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$. 
%\Clifton{I still need to confirm this claim.}
%Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
%\end{proof}

@@

\begin{definition}
An object in $\QC(\GN{T})$ is an equivalence class in $\cup_{n} \obj \QC(\GN{T}_n)$ under the relation: $\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$. Objects in $\QC(\GN{T})$ all take the form
\[
[\qcs{L}_n] \ceq \{ f_{n\leq k}^* \qcs{L}_n \tq n\leq k\},
\]
for some unique $\qcs{L}_n \in \QC(\GN{T}_n)$.
Maps $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ are defined as follows:
$\Hom([\qcs{L}_n],[\qcs{L}_m])$ is the set of equivalence classes in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$ under the relation: $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to $\beta_l \in \QC(\GN{T}_l)$ if $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$ for some $k,l\leq i$. Maps in $\QC(\GN{T})$ all take the form
\[
[\alpha_k] \ceq \{ f_{k\leq i}^* \alpha_k \tq k\leq i\},
\]
for some unique $\alpha_k \in \QC(\GN{T}_k)$.
Identities and composition are defined in the natural way.
We refer to objects in $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} or \emph{quasicharacter sheaves for $T$}.
\end{definition}

Category $\QC(\GN{T})$ carries a tensor structure under
\[
[\qcs{L}_n]\otimes [\qcs{L}_m] \ceq [f_{n\leq k}^*\qcs{L}_n \otimes f_{m\leq k}^*\qcs{L}_m],
\qquad k = \max\{ n,m\}.
\]
Duals in $\QC(\GN{T})$ are defined by $[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee]$.

@@

\section{Toward geometric reciprocity}

@@

\begin{proof}
Weil restriction behaves properly with respect to formation of Néron models:
there is a canonical isomorphism
\[
\underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
\]
And Weil restriction behaves properly with respect to the Greenberg transform:
there is a canonical isomorphism 
\Clifton{Really?}
\[
\Gr_{n} \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})
\iso
\Res_{k'/k} \Gr_n(\underline{T'}),
\]
where $k'$ is the residue field for $K'$.
And the Greenberg tranforms respects products:
\[
\Gr_n(\underline{T'}) = \Gr_n(\underline{T})\times_{k} {k'}.
\]
Now use Proposition~\ref{prop:csbe}.
\end{proof}

>>>>

We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
Analogous sheaves on connected, commutative algebraic groups were first studied
by Deligne \cite{deligne:SGA4.5}, \David{more specific citation} and more recently Drinfeld has referred to such objects
as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
is a direct generalization of the sheaf--function dictionary to the case of commutative
group schemes which are not necessarily connected or finite type.  The main use
of the term ``character sheaf'' is due to Lusztig \cite{lusztig:85a}*{Def.~2.10}.  Most of his energy is devoted to
handling non-commutative groups; though he does define character sheaves for some
non-connected groups he restricts his attention to reductive groups with cyclic component group, which are extensions of $\ZZ/n\ZZ$ by a torus. 
In this case is not difficult to relate his Frobenius-stable character sheaves to our quasicharacter sheaves.

We close the introduction with a more detailed description of the structure of this paper.
In Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
them as Weil sheaves with a Galois action.
Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism,
one direction of the sheaf--function dictionary.
We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
them to prove a functoriality result on the trace of Frobenius.
In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
and Weil restriction.
Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded and finite quasicharacter sheaves,
two subcategories of $\QC(G)$.  These alternate descriptions of quasicharacter sheaves play a key
role in the proof of Proposition~\ref{prop:restriction}.
In section \ref{sec:connected} we show that bounded and finite quasicharacter sheaves are the same
as standard quasicharacter sheaves when $G$ is connected, and that trace of Frobenius is an isomorphism.
We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and give a more concrete interpretation
of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
we give an isomorphism between $\QCiso{G}$ and $\Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))$.
Section~\ref{sec:etalecohom} proves a result in Galois cohomology that shows that trace of Frobenius is
an isomorphism for \'etale group schemes.
In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
induces an essentially surjective functor of quasicharacter sheaves.
Section~\ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem: trace of Frobenius
is an isomorphism for $G$ as long as the geometric component group is finitely generated.

In Section~\ref{sec:GN} we introduce N\'eron models of tori and the Greenberg transform, which produce
group schemes over $\Fq$ from algebraic tori $T$ over $K$.
Section~\ref{sec:bdchar} then uses Theorem~\ref{thm:snake} to give a geometrization of characters of $T$
of bounded depth.
We give a reinterpretation of this result in Section~\ref{sec:quasichar}, using a limit process to simultaneously
geometrize all quasicharacters of $T$.  Sections~\ref{sec:bdchar} and \ref{sec:quasichar} also include
functoriality results that we hope to use in a future discussion of class field theory.
In Section~\ref{sec:transfer} we discuss a transfer principle which allows
a geometric transfer of characters between characteristic $p$ tori to characteristic $0$ tori.
We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter sheaves may play a key role in a geometric and categorical form of the local Langlands correspondence for algebraic tori over non-archimedean local fields.

@@

  We now show that $[\tau_\qcs{L}]$ depends only on the isomorphism class of $\qcs{L}$.
  Let $\alpha : \qcs{L} \to \qcs{L'}$ be an isomorphism and
  let $\tau$ and $\tau'$ be any cocycles representing the classes in the
  image of $\qcs{L}$ and $\qcs{L'}$ under \eqref{cohomologous}; by construction,
  $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$ 
  according to Lemma~\ref{lemma:section}.
    Now, $\varphi_x(s(x))$ is a
  non-zero scalar multiple of $s'(x)$; define $a: G(\bFq) \to \EEx$
  by $\alpha_x(s(x)) = a(x) s'(x)$.
  By the second part of condition~\ref{cs.3},
  $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$,
  %\Clifton{Fix this.}
  so $\tau$ and $\tau'$ are cohomologous. This shows that
  \begin{equation}\label{pich1}
    \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*), \qquad \qcs{L}_{/\text{iso}} \mapsto [\tau_\qcs{L}]
  \end{equation}
  is well-defined.

@@

Recall that $\Fq$ is a finite field.
Let $K$ be a non-archimedean local field with residue field $\Fq$.
We place no restriction on the characteristic of $K$. 
We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
Let $T$ be an algebraic torus over $K$.
We write $\Hom_{< n}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $n$ 
and $\Hom_{\text{qc}}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth;
we call these quasicharacters of $T(K)$, following \cite{tate:67a}*{2.3}.

@@

For any positive integer $n$, let
\[
%\begin{tikzcd}
\Gr_n : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\Fq$}\right)
%\end{tikzcd}
\]
be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^n$ with the Greenberg functor.
The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ 
%\Clifton{Do you think I should say more about $P_{n}$?}
\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
For a given Néron model $\TT$ of $T$, set
\[
\GN{T}_n \ceq \Gr_n(\TT)
\qquad \text{and}\qquad
f_n \ceq P_n(\TT).
\]
%
\Clifton{I guess this next bit needs to be re-structured.}
Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
 \begin{enumerate}
   \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
  \labitem{(GN.1)}{smooth} $\GN{T}_n$ is a smooth commutative group scheme
  locally of finite type over $\Fq$ and the component group of $\GN{T}_n$ is
  geometrically finitely generated: $\underline{T}$ is a smooth group scheme over $\OK$, by construction; since smoothness is preserved under base change, $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ is a smooth group scheme over an Artinian ring with perfect residue field; the Greenberg functor preserves smoothness, so $\GN{T}_n$ is a smooth group scheme over $\Fq$; the identity component of any smooth group scheme is geometrically connected, hence connected, and the Greenberg functor takes the geometric identity component of $\TT_n$ to the geometric identity component of $\GN{T}_n$;
  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
  this group is finitely generated by \cite{xarles:93a}*{2.18}.
  \labitem{(GN.2)}{truncation}
  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes. To see this, it suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$. Base change along $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a closed immersion of schemes $\TT_{n+1} \hookrightarrow \TT_n$ (not a morphism of group schemes). Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$. 
\Clifton{I still need to confirm this claim.}
Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
  \end{enumerate}
%
We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.

@@

For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
\Clifton{Now I wonder if $f_{n\leq m}$ is a discrete isogeny!!! 
What's the covering group of $f_{n\leq m}$? 
Must be the finite group $\GN{T}_{m}(\Fq)/\GN{T}_n(\Fq)$, which could be $\TT^0(\pK^n/\pK^{m})$. 
We might be able to build some very special finite quasicharacter sheaves on $\GN{T}_n$ this way.}
Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor promised by Proposition~\ref{prop:pullback}.
%
%\begin{proposition}\label{prop:nm}
The functor $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ is full and faithful, by \ref{truncation}.
%\end{proposition}
%
%\begin{proof}
%
%\end{proof}

@@

\begin{definition}
An object in $\QC(\GN{T})$ is an equivalence class in $\cup_{n} \obj \QC(\GN{T}_n)$ under the relation: $\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$. Objects in $\QC(\GN{T})$ all take the form
\[
[\qcs{L}_n] \ceq \{ f_{n\leq k}^* \qcs{L}_n \tq n\leq k\},
\]
for some unique $\qcs{L}_n \in \QC(\GN{T}_n)$.
Maps $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ are defined as follows:
$\Hom([\qcs{L}_n],[\qcs{L}_m])$ is the set of equivalence classes in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$ under the relation: $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to $\beta_l \in \QC(\GN{T}_l)$ if $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$ for some $k,l\leq i$. Maps in $\QC(\GN{T})$ all take the form
\[
[\alpha_k] \ceq \{ f_{k\leq i}^* \alpha_k \tq k\leq i\},
\]
for some unique $\alpha_k \in \QC(\GN{T}_k)$.
Identities and composition are defined in the natural way.
Category $\QC(\GN{T})$ carries a tensor structure under
\[
[\qcs{L}_n]\otimes [\qcs{L}_m] \ceq [f_{n\leq k}^*\qcs{L}_n \otimes f_{m\leq k}^*\qcs{L}_m],
\qquad k = \max\{ n,m\}.
\]
Duals in $\QC(\GN{T})$ are defined by $[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee]$.
We refer to objects in the rigid symmetric monoidal category $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} or \emph{quasicharacter sheaves for $T$}.
\end{definition}

@@

\section{Toward geometric reciprocity}
\label{sec:reciprocity}

@@

\begin{proof}
Weil restriction behaves properly with respect to formation of Néron models:
there is a canonical isomorphism
\[
\underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
\]
And Weil restriction behaves properly with respect to the Greenberg transform:
there is a canonical isomorphism 
\Clifton{References needed!}
\[
\Gr_{n} \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})
\iso
\Res_{k'/k} \Gr_n(\underline{T'}),
\]
where $k'$ is the residue field for $K'$.
And the Greenberg tranforms respects products:
\[
\Gr_n(\underline{T'}) = \Gr_n(\underline{T})\times_{k} {k'}.
\]
Now use Proposition~\ref{prop:csbe}.
\end{proof}
